\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
bib and proposal update

The dataset we use originated from a project that researched classifying cognitive state using Gaussian Naive Bayes classifiers. This resulted in an accuracy of approximately 85\%. According to literature\footnote{Bayesian network classifiers - N. Friedman, D. Geiger, and M. Goldszmidt}, a higher accuracy could be obtained by using a so-called \textit{Tree Augmented Naive Bayesian network classifier}, or TAN. We will use this classification method to investigate whether we are indeed able to reach a higher accuracy.

@@

Describe the different phases and the planning deadlines (until November)

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the model will be realised.
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation ...
	\item[20th - 22nd October]\-\\
	Preparing the presentation ...
	\item[28th October]\-\\
	Final delivery of the document and the implementation
\end{description}

%\cite{Friedman:1997gw}
\nocite{*} %DO NOT UNCOMMENT, only for test purpose
\bibliographystyle{IEEEtran}
\bibliography{bibliography}

>>>>

The dataset we use originated from a project that researched classifying cognitive state using Gaussian Naive Bayes classifiers. This resulted in an accuracy of approximately 85\%. According to literature \cite{Friedman:1997gw}, a higher accuracy could be obtained by using a so-called \textit{Tree Augmented Naive Bayesian network classifier}, or TAN. We will use this classification method to investigate whether we are indeed able to reach a higher accuracy.

@@

In this section we describe the various phases and the planning deadlines that the group will follow.

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the various models will be realised.
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation ...
	\item[20th - 22nd October]\-\\
	During this time period the group members will prepare the presentation of the project.
	\item[28th October]\-\\
	Until the aforementioned date the final version of the document and the implementation will be delivered.
\end{description}

\nocite{*} %DO NOT UNCOMMENT, only for test purpose
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
